## Kernel estimator {#sec-kernel}

**UPDATE**: In this section, I compare the rejection frequencies of using a demeaned outcome variable or not, and using the same data vs using different data. I use 1,000 iterations. 

@tbl-kernel-same displays the rejection frequencies for both models, using the same data.

@tbl-kernel-same displays the rejection frequencies for both models, using different data. 


I compare the results for the three different variance estimators, the HR, SCPC, and Kernel. For the Kernel estimator, I try different cut-off distances. In addition, B-Splines of different order and quantities are introduced to help improve the rejection frequency of the Kernel estimator.

In the DGP, $e_l\sim\mathcal{G}_{exp}(c_{\bar\rho})$ and $X\sim[1 \;\mathcal{G}_{exp}(c_{\bar\rho}) \;\mathcal{G}_{exp}(c_{\bar\rho})]$. The average pairwise correlation is $\bar\rho=0.03$. 

In the estimation process, Model 2 uses a demeaned outcome variable, whereas Model 1 does not. I'm using one and two-order splines (step functions and triangles). In addition, I'm using a Cholesky decomposition to invert the covariates matrix in the OLS estimator.

For every draw and every ols regression, I estimated an AR(1) model using the residuals $\hat{e}_{l+1}=\gamma_0+\gamma_1 \hat{e}_l + u_l$, after sorting from closest to zero to closest to one. 

I used 1000 iterations to calculate the rejection frequencies and the average AR(1) coefficients of the residuals.





```{r}
#| label: tbl-kernel-same
#| tbl-cap: Rejection frequencies comparing using or not a demeaned outcome variable for the same data. 1000 iterations.
#| tbl-cap-location: bottom
#| echo: false
#| warning: false

kernel_results <- read.csv("../Simulations/Products/crank_bs_ear1_sims_res_same.csv")

# row_names <- c(
#     " ",
#     "HR",
#     "SCPC",
#     "0.01",
#     "0.03",
#     "0.05",
#     "0.07",
#     "0.01",
#     "0.03",
#     "0.05",
#     "0.07"
# )

row_names <- c(
    # " ",
    "HR",
    "SCPC",
    rep(
        c(
            "0.015",
            "0.030",
            "0.050"
            # "0.07"
        ),
        9
    )
)

col_names <- c(
    "Estimator",
    rep(
        c(
            "Cons.",
            "$\\beta_1$"#,
            # "$\\beta_2$"
        ),
        2
    )
)

table <- cbind(row_names, kernel_results)

kbl(
    table, 
    digits=3, 
    booktabs = TRUE,
    col.names = col_names,
    # row.names = row_names,
    escape = F
    ) %>%
    add_header_above(
        c(" ","Model 1"=2,"Model 2"=2)
    ) %>%
    pack_rows(
        "Kernel",3,5
    ) %>%
    pack_rows(
        "B-Splines order 1 (Step functions)",6,17, latex_align = "l", hline_after = TRUE
    ) %>%
    pack_rows(
        "B-Splines order 2 (Triangles)",18,29, latex_align = "l", hline_after = TRUE
    ) %>%
    pack_rows(
        "Kernel + B-S, 4 splines",6,8
    ) %>%
    pack_rows(
        "Kernel + B-S, 12 splines",9,11
    ) %>%
    pack_rows(
        "Kernel + B-S, 24 splines",12,14
    ) %>%
    pack_rows(
        "Kernel + B-S, 36 splines",15,17
    ) %>%
    pack_rows(
        "Kernel + B-S, 4 splines",18,20
    ) %>%
    pack_rows(
        "Kernel + B-S, 12 splines",21,23
    ) %>%
    pack_rows(
        "Kernel + B-S, 24 splines",24,26
    ) %>%
    pack_rows(
        "Kernel + B-S, 36 splines",27,29
    ) #%>%
 



```


```{r}
#| label: tbl-kernel-diff
#| tbl-cap: Rejection frequencies comparing using or not a demeaned outcome variable for different data. 1000 iterations.
#| tbl-cap-location: bottom
#| echo: false
#| warning: false

kernel_results <- read.csv("../Simulations/Products/crank_bs_ear1_sims_res_diff.csv")

# row_names <- c(
#     " ",
#     "HR",
#     "SCPC",
#     "0.01",
#     "0.03",
#     "0.05",
#     "0.07",
#     "0.01",
#     "0.03",
#     "0.05",
#     "0.07"
# )

row_names <- c(
    # " ",
    "HR",
    "SCPC",
    rep(
        c(
            "0.015",
            "0.030",
            "0.050"
            # "0.07"
        ),
        9
    )
)

col_names <- c(
    "Estimator",
    rep(
        c(
            "Cons.",
            "$\\beta_1$"#,
            # "$\\beta_2$"
        ),
        2
    )
)

table <- cbind(row_names, kernel_results)

kbl(
    table, 
    digits=3, 
    booktabs = TRUE,
    col.names = col_names,
    # row.names = row_names,
    escape = F
    ) %>%
    add_header_above(
        c(" ","Model 1"=2,"Model 2"=2)
    ) %>%
    pack_rows(
        "Kernel",3,5
    ) %>%
    pack_rows(
        "B-Splines order 1 (Step functions)",6,17, latex_align = "l", hline_after = TRUE
    ) %>%
    pack_rows(
        "B-Splines order 2 (Triangles)",18,29, latex_align = "l", hline_after = TRUE
    ) %>%
    pack_rows(
        "Kernel + B-S, 4 splines",6,8
    ) %>%
    pack_rows(
        "Kernel + B-S, 12 splines",9,11
    ) %>%
    pack_rows(
        "Kernel + B-S, 24 splines",12,14
    ) %>%
    pack_rows(
        "Kernel + B-S, 36 splines",15,17
    ) %>%
    pack_rows(
        "Kernel + B-S, 4 splines",18,20
    ) %>%
    pack_rows(
        "Kernel + B-S, 12 splines",21,23
    ) %>%
    pack_rows(
        "Kernel + B-S, 24 splines",24,26
    ) %>%
    pack_rows(
        "Kernel + B-S, 36 splines",27,29
    ) #%>%
 



```


