## Evenly spaced locations (time series)

In this exercise, locations are evenly spaced from $\frac{1}{250}$ to 1. The error terms and the regressors are autocorrelated following an AR(1) process $e_{l+1}=\gamma e_l+ u_l$, where $u_l\sim N(0,1)$, and $\gamma=0.79$. Likewise, $x_{l+1}=\lambda x_l+ v_l$, where $v_l\sim N(0,1)$, and $\lambda=0.79$. The DGP for y is therefore, $y_l=\beta_0+\beta_1 x_l+e_l$ with $(\beta_0, \beta_1)=(1, 1.5)'$.

@tbl-grid-all displays the rejection frequencies of 1000 simulations. SCPC is omitted because it could not find a reasonable value of $c_{min}$ for the default value of $\bar\rho=0.03$ with the evenly distributed locations. In addition, the table also displays $\gamma_1$, the average slope coefficient of an AR(1) model using the residuals of the OLS regression for every iteration, and the BIC for two methods as described in @sec-kernel.


```{r}
#| label: tbl-grid-all
#| tbl-cap: Rejection frequencies for different variance estimators. Time series data with evenly distributed locations. 250 obs. 1000 iterations.
#| echo: false
#| warning: false


kernel_results <- read.csv("../Simulations/Products/grid_sims_res_dd_2x.csv")

e_ar1_tbl <- read.csv("../Simulations/Products/grid_sims_ar1_dd_2x.csv")

dist_v_tbl <- read.csv("../Simulations/Products/grid_sims_dist_v_dd_2x.csv")

aux0 <- c(
    # " ",
    # "SCPC",
    rep(
        c(
            "HR",
            "Kernel ",
            "Kernel ",
            "Kernel "
            # "0.07"
        ),
        1
    ),
    rep(
        c(
            "HR",
            "Kernel ",
            "Kernel ",
            "Kernel ",
            "Damian's "
            # "0.07"
        ),
        16
    )
)
dist_tbl <- c(
    rep(
        "",
        1
    ),
    "0.015",
    "0.030",
    "0.080",
    gsub("NaN"," ", round(dist_v_tbl[[1]],3))
)
row_names_kernel <- paste0(aux0,dist_tbl)
row_names_ar1_kernel <- c(
    rep(
        "No splines",
        4
    ),
    rep(
        c(
        "4 splines",
        "8 splines",
        "12 splines",
        "24 splines",
        "36 splines",
        "48 splines",
        "60 splines",
        "72 splines"#,
        # "88 splines",
        # "124 splines"
        ),
        each=5,
        times =2
    )
)
aux <- c(
    rep(
        "",
        4
    ),
    rep(
        c(
            "Order 1",
            "Order 2"
        ),
        each = 40
    )
)
kernel_id<-paste0(aux, row_names_ar1_kernel)

table_kernel <- cbind(
    aux,
    row_names_ar1_kernel,
    row_names_kernel, 
    kernel_results, 
    kernel_id
)
names(table_kernel)<- c(
    "Order", "Qty.",
    "Estimator",
    "Cons.",
    "$\\beta_1$",
    "id"
)

row_names_ar1 <- c(
    "No splines",
    rep(
        c(
        "4 splines",
        "8 splines",
        "12 splines",
        "24 splines",
        "36 splines",
        "48 splines",
        "60 splines",
        "72 splines"#,
        # "88 splines",
        # "124 splines"
        ),
        2
    )
)
aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1",
            "Order 2"
        ),
        each = 8
    )
)
ar1_id<-paste0(aux2, row_names_ar1)
table_ar1 <-cbind(
    ar1_id,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "id",
    "Cons2",
    "$\\gamma$",
    "Hansen's",
    "Damian's"
)

table<-merge(table_kernel,table_ar1, by="id",sort=FALSE)

kbl(
    table[, -c(1,7)], 
    digits=3, 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F
    ) %>%
    add_header_above(
        c("B-Splines"=2,"T.S. data"=3," "=1,"BIC"=2)#,"Model 2"=2)
    ) %>%
    add_header_above(
        c(" "=5,"Residuals"=3)
    ) %>%
    collapse_rows(
        c(1:2,6:8),
        latex_hline = "custom",
        custom_latex_hline = 1:2,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```

@tbl-rho-bar-ar1 displays the average pairwise correlation for groups of different cut-off distances. The average pairwise correlation was estimated as follows 

$$
\bar\rho=(T(T-1))^{-1}\Sigma_{l=1}^T\Sigma_{l\not=\text{l}}^T[e_le_{\text{l}}\mathbb{I}(|s_l-s_{\text{l}}|<L)]
$$



```{r}
#| label: tbl-rho-bar-ar1
#| tbl-cap: Average pairwise correlation within observations of groups for different distances. $\bar\rho=(T(T-1))^{-1}\Sigma_{l=1}^T\Sigma_{l\not=\text{l}}^T[e_le_{\text{l}}\mathbb{I}(|s_l-s_{\text{l}}|<L)]$
#| echo: false
#| warning: false


rho_bar_groups <- read.csv("../Simulations/Products/pairwise_corr.csv")

# row_names <- c(
#     "0.01",
#     "0.05",
#     "0.10",
#     "0.50"
# )

col_names <- c(
    "Distance",
    "$\\bar\\rho$"
)

# rho_tbl <- cbind(row_names, rho_bar_groups)

kbl(
    rho_bar_groups,
    digits=3, 
    booktabs = TRUE,
    col.names = col_names,
    escape = F
)

```
