## Highly concentrated locations

In this exercise, locations are highly concentrated in a few spots. First, 25 points were generated randomly in the unit square. Then, around these "parent" points, 10 random "children" points were drawn uniformly from a 0.01 radius circle. The "children" points were used as the true locations.

@tbl-hc-locs-me displays the rejection frequencies for the different estimators when ME radius is 0.03. @tbl-hc-locs-me-rho displays the rejection frequencies when the DGP's average pairwise correlation $\bar\rho$ (0.06) is higher than the C-SCPC/SCPC's $\bar\rho_{max}$ (0.03). @tbl-hc-locs-me-rho-below displays the rejection frequencies when the DGP's average pairwise correlation $\bar\rho$ (0.01) is lower than the C-SCPC/SCPC's $\bar\rho_{max}$ (0.03). @fig-hist-light-locs displays the histogram of the distances using the true and mismeasured locations.

When the locations are drawn from highly concentrated distribution and ME radius is 3 percent, the rejection frequencies of MW's method increase non-trivially. C-SCPC increases from 4 to 6 percent, and SCPC to 7 (constant) and 10 (slope) percent. When, in addition to the ME, the DGP's average pairwise correlation is larger than the specified by the MW's method, the increase in the rejection frequencies is even larger. When the DGP's average pairwise correlation is lower (0.01) than MW's (0.03), the rejection frequencies are not bad.

The KerneL+B SPlines method also suffers. Rejection frequencies increase as the CI lengths. Because the locations are less informative about the correlation between neighbouring observations, the method struggles to achieve the desired NN correlation in the residuals, leading to higher rejection frequencies.

```{r}
#| label: tbl-hc-locs-me
#| tbl-cap: Rejection frequencies for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.03. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| echo: false
#| warning: false
#| eval: true
#| include: true

kernel_results <- read.csv("../Simulations/Products/opt_spline_sims_res_light_locs_me_3p_matching.csv")

e_ar1_tbl <- read.csv("../Simulations/Products/opt_spline_sims_ar1_light_locs_me_3p_matching.csv")

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    rep(
        c(
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050"#,
            # "Damian's"
        ),
        1
    ),
        rep(
        c(
            "HR",
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050",
            "Damian's (x2)",
            "Damian's (x3)"

        ),
        1
    )
)
# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        4+2
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_kernel <- cbind(
    aux,
    row_names_kernel, 
    kernel_results#, 
)
names(table_kernel)<- c(
    "Splines",
    "Estimator",
    "Cons.",
    "$\\beta_1$",
    "Cons. ",
    "$\\beta_1$ ",
    "$i$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Slope",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_kernel,table_ar1, by="Splines",sort=FALSE)

kbl(
    table[,-c(9,11)], #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=4,"C.I. length"=2)
    ) %>%
    add_header_above(
        c(" "=1,"Spatial data"=6,"Residuals"=3)
    ) %>%
    collapse_rows(
        c(1,8:10),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```


```{r}
#| label: tbl-hc-locs-me-rho
#| tbl-cap: Rejection frequencies for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.06. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| echo: false
#| warning: false
#| eval: true
#| include: true

kernel_results <- read.csv("../Simulations/Products/opt_spline_sims_res_light_locs_me_3p_true_rho_above.csv")

e_ar1_tbl <- read.csv("../Simulations/Products/opt_spline_sims_ar1_light_locs_me_3p_true_rho_above.csv")

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    rep(
        c(
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050"#endregion,
            # "Kernel 0.060"
            # "Damian's"
        ),
        1
    ),
        rep(
        c(
            "HR",
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050",
            # "Kernel 0.060",
            "Damian's (x2)",
            "Damian's (x3)"

        ),
        1
    )
)
# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        7-1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_kernel <- cbind(
    aux,
    row_names_kernel, 
    kernel_results#, 
)
names(table_kernel)<- c(
    "Splines",
    "Estimator",
    "Cons.",
    "$\\beta_1$",
    "Cons. ",
    "$\\beta_1$ ",
    "$i$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Slope",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_kernel,table_ar1, by="Splines",sort=FALSE)

kbl(
    table[,-c(9,11)], #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=4,"C.I. length"=2)
    ) %>%
    add_header_above(
        c(" "=1,"Spatial data"=6,"Residuals"=3)
    ) %>%
    collapse_rows(
        c(1,8:10),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```

```{r}
#| label: tbl-hc-locs-me-rho-below
#| tbl-cap: Rejection frequencies for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.01. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| echo: false
#| warning: false
#| eval: true
#| include: true

kernel_results <- read.csv("../Simulations/Products/opt_spline_sims_res_light_locs_me_3p_true_rho_below.csv")

e_ar1_tbl <- read.csv("../Simulations/Products/opt_spline_sims_ar1_light_locs_me_3p_true_rho_below.csv")

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    rep(
        c(
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050"#endregion,
            # "Kernel 0.060"
            # "Damian's"
        ),
        1
    ),
        rep(
        c(
            "HR",
            "Kernel 0.015",
            "Kernel 0.030",
            "Kernel 0.050",
            # "Kernel 0.060",
            "Damian's (x2)",
            "Damian's (x3)"

        ),
        1
    )
)
# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        7-1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_kernel <- cbind(
    aux,
    row_names_kernel, 
    kernel_results#, 
)
names(table_kernel)<- c(
    "Splines",
    "Estimator",
    "Cons.",
    "$\\beta_1$",
    "Cons. ",
    "$\\beta_1$ ",
    "$i$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Slope",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_kernel,table_ar1, by="Splines",sort=FALSE)

kbl(
    table[,-c(9,11)], #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=4,"C.I. length"=2)
    ) %>%
    add_header_above(
        c(" "=1,"Spatial data"=6,"Residuals"=3)
    ) %>%
    collapse_rows(
        c(1,8:10),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```


![Histogram of distances, locations drawn from a highly
concentrated spatial distribution]("../Simulations/Products/hist_dist_light_locs_me_3p.png"){#fig-hist-light-locs}