## Ideal Confidence Intervals

How wide should the Confidence Intervals should be to get a rejection frequency of 5 percent? After running the simulations as described in @sec-high-concentrated-locs, I used the distribution of the $t$ statistic to get the values of the 2.5 and 97.5 percentile. The tables in this section report the difference between the two values. 

In addition, to make the tables reported in this section easily comparable with @sec-high-concentrated-locs, the tables also report the value of the difference times the absolute value of the average standard error.

Lastly, the tables also include the statistics requested by Tim. Tim's statistic is the sum of the off-diagonal elements of the $XX'$ covariates matrix divided by the sum of the diagonal elements.

```{r}
#| label: tbl-lights-me-matching-rhos
#| tbl-cap: 5 percent CI lengths for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.03. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| eval: true
#| include: true

excercise <- "light_locs_me_3p_matching_rhos_tims_stat"

# kernel_results <- read.csv(
#     paste0(products_folder,"opt_spline_sims_res_", excercise,".csv")
# )

e_ar1_tbl <- read.csv(
    paste0(products_folder,"opt_spline_sims_ar1_", excercise, ".csv")
)

optimal_CI_table <- read.csv(
    paste0(products_folder, "opt_ci_table_", excercise, ".csv")
)

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "HR",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "Damian's (x2)",
    "Damian's (x3)"
)

# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        4+2
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_ci <- cbind(
    aux,
    row_names_kernel, 
    optimal_CI_table
)
names(table_ci)<- c(
    "Splines",
    "Estimator",
    "Cons. Z",
    "$\\beta_1$ Z",
    "Cons.",
    "$\\beta_1$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Tim's Stat",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_ci,table_ar1[,c(1,3)], by="Splines",sort=FALSE)

kbl(
    table, #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=2,"C.I. length"=4)
    ) %>%
    # add_header_above(
    #     c(" "=1,"Spatial data"=6,"Residuals"=3)
    # ) %>%
    collapse_rows(
        c(1,7),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```


```{r}
#| label: tbl-lights-me-true-rho-above
#| tbl-cap: 5 percent CI lengths for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.06. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| eval: true
#| include: true

excercise <- "light_locs_me_3p_true_rho_above_tims_stat"

# kernel_results <- read.csv(
#     paste0(products_folder,"opt_spline_sims_res_", excercise,".csv")
# )

e_ar1_tbl <- read.csv(
    paste0(products_folder,"opt_spline_sims_ar1_", excercise, ".csv")
)

optimal_CI_table <- read.csv(
    paste0(products_folder, "opt_ci_table_", excercise, ".csv")
)

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "HR",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "Damian's (x2)",
    "Damian's (x3)"
)

# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        4+2
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_ci <- cbind(
    aux,
    row_names_kernel, 
    optimal_CI_table
)
names(table_ci)<- c(
    "Splines",
    "Estimator",
    "Cons. Z",
    "$\\beta_1$ Z",
    "Cons.",
    "$\\beta_1$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Tim's Stat",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_ci,table_ar1[,c(1,3)], by="Splines",sort=FALSE)

kbl(
    table, #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=2,"C.I. length"=4)
    ) %>%
    # add_header_above(
    #     c(" "=1,"Spatial data"=6,"Residuals"=3)
    # ) %>%
    collapse_rows(
        c(1,7),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```



```{r}
#| label: tbl-lights-me-true-rho-below
#| tbl-cap: 5 percent CI lengths for different variance estimators. Spatial data with highly concentrated two-dimensional mismeasured locations. Selecting the number of B Splines using the lowest Nearest Neighbour (NN) correlation in residuals from a grid going from 4 to 12 splines. ME radius is 3 percent. DGP's $\bar\rho$ is 0.01. C-SCPC/SCPC $\bar\rho_{max}$ is 0.03.
#| eval: true
#| include: true

excercise <- "light_locs_me_3p_true_rho_below_tims_stat"

# kernel_results <- read.csv(
#     paste0(products_folder,"opt_spline_sims_res_", excercise,".csv")
# )

e_ar1_tbl <- read.csv(
    paste0(products_folder,"opt_spline_sims_ar1_", excercise, ".csv")
)

optimal_CI_table <- read.csv(
    paste0(products_folder, "opt_ci_table_", excercise, ".csv")
)

# notes <- c(rep("",5),"$^a$",rep("",9),"$^b$")
row_names_kernel<- c(
    "HR",
    "SCPC",
    "C-SCPC",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "HR",
    "Kernel 0.015",
    "Kernel 0.030",
    "Kernel 0.050",
    "Damian's (x2)",
    "Damian's (x3)"
)

# row_names_kernel_notes <-paste0(row_names_kernel,notes)
aux <- c(
    rep(
        "",
        4+2
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        each = 6
    )
)

table_ci <- cbind(
    aux,
    row_names_kernel, 
    optimal_CI_table
)
names(table_ci)<- c(
    "Splines",
    "Estimator",
    "Cons. Z",
    "$\\beta_1$ Z",
    "Cons.",
    "$\\beta_1$"
)

aux2 <- c(
    rep(
        "",
        1
    ),
    rep(
        c(
            "Order 1"#,
            # "Order 2"
        ),
        1
    )
)

table_ar1 <-cbind(
    aux2,
    e_ar1_tbl
)
names(table_ar1)<-c(
    "Splines",
    "NN",
    "Tim's Stat",
    "BIC",
    "Damian's",
    "Dropped"
)
table<-merge(table_ci,table_ar1[,c(1,3)], by="Splines",sort=FALSE)

kbl(
    table, #- id, 
    digits=3,#c(3,3,5,3), 
    booktabs = TRUE,
    longtable = TRUE,
    # col.names = col_names,
    # row.names = row_names,
    escape = F,
    position = "p"#,
    # format.args = list(scientific=TRUE)
    ) %>%
    add_header_above(
        c(" "=2,"C.I. length"=4)
    ) %>%
    # add_header_above(
    #     c(" "=1,"Spatial data"=6,"Residuals"=3)
    # ) %>%
    collapse_rows(
        c(1,7),
        latex_hline = "custom",
        custom_latex_hline = 1,
        valign = "top"#,
        # row_group_label_position = "stack"
    ) #%>%

```
