# 8x8 Quadratic B-Spline {#sec-8x8}

@tbl-HAC-8x8 and @tbl-HAC-8x8-u show the rejection frequencies of testing the null hypothesis $H_0=\hat\beta_0-\beta_0$ for different values of $\rho$ adding an 8x8 quadratic B-Spline for the triangle and uniform kernel HAC.

@tbl-HAC-8x8-unif-bs and @tbl-HAC-8x8-u-unif-bs show the same exercise but using an 8x8 step function B-Splines for the triangle and uniform kernel HAC.

@tbl-HAC-8x8-ci and @tbl-HAC-8x8-u-ci show the confidence interval lengths for the same simulations of tables [-@tbl-HAC-8x8] and [-@tbl-HAC-8x8-u]. Likewise, @tbl-HAC-8x8-ci-unif-bs and @tbl-HAC-8x8-u-ci-unif-bs show the confidence interval lengths for tables @tbl-HAC-8x8-unif-bs and @tbl-HAC-8x8-u-unif-bs.

In addition, the tables show the rejection frequencies when using the heteroscedastic robust variance for the standard error à la Stata and the BIC.

BIC [@Hansen2020] is estimated as
$$
BIC_H=T\log(2\pi\hat{\sigma}^2_{e_l})+T+(k+1)\log(T)
$$ {#eq-hansen-bic}

```{r}
#| label: tbl-HAC-8x8
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **quadratic** B-splines and the **triangle** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).
#| eval: false
#| include: false


exe<-'8x8_quad_splines_'

tbl_quad_bs_s<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope.csv'
    )
)

kbl(
    tbl_quad_bs_s,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Quad-BS'=ncol(tbl_quad_bs_s)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s))
)

```

```{r}
#| label: tbl-HAC-8x8-u
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **quadratic** B-splines and the **uniform** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).
#| eval: false
#| include: false

tbl_quad_bs_s_u<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u.csv'
    )
)

kbl(
    tbl_quad_bs_s_u,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Quad-BS'=ncol(tbl_quad_bs_s_u)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u))
)

```

```{r}
#| label: tbl-HAC-8x8-unif-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **uniform** B-splines and the **triangle** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


exe<-'8x8_no_cons_unif_bs_keep_'

tbl_quad_bs_s<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope.csv'
    )
)

kbl(
    tbl_quad_bs_s,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Unif-BS'=ncol(tbl_quad_bs_s)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s))
)

```

```{r}
#| label: tbl-HAC-8x8-u-unif-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **uniform** B-splines and the **uniform** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


tbl_quad_bs_s_u<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u.csv'
    )
)

kbl(
    tbl_quad_bs_s_u,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Unif-BS'=ncol(tbl_quad_bs_s_u)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u))
)

```


```{r}
#| label: tbl-HAC-8x8-ci
#| tbl-cap: Confidence Interval length of using the **triangle** kernel HAC variance estimator for the standard error after adding an 8x8 **quadratic** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


exe<-'8x8_quad_splines_'

tbl_quad_bs_s_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Quad-BS'=ncol(tbl_quad_bs_s_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_ci))
)

```

```{r}
#| label: tbl-HAC-8x8-u-ci
#| tbl-cap: Confidence Interval length of using the **uniform** kernel HAC variance estimator for the standard error after adding an 8x8 **quadratic** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


tbl_quad_bs_s_u_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_u_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Quad-BS'=ncol(tbl_quad_bs_s_u_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u_ci))
)

```


```{r}
#| label: tbl-HAC-8x8-ci-unif-bs
#| tbl-cap: Confidence Interval length of using the **triangle** kernel HAC variance estimator for the standard error after adding an 8x8 **uniform** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).

exe<-'8x8_unif_splines_'

tbl_quad_bs_s_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Quad-BS'=ncol(tbl_quad_bs_s_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_ci))
)

```

```{r}
#| label: tbl-HAC-8x8-u-ci-unif-bs
#| tbl-cap: Confidence Interval length of using the **uniform** kernel HAC variance estimator for the standard error after adding an 8x8 **uniform** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


tbl_quad_bs_s_u_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_u_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Quad-BS'=ncol(tbl_quad_bs_s_u_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u_ci))
)

```

