---
title: "Replication - Morgan"
number-sections: true
author: Hans Martinez
date: today
bibliography: biblio.bib
format:
    pdf:
        documentclass: article
        colorlinks: true
        include-in-header: packages.tex
        keep-tex: true
        resource-path: 
            - "../outputs"
        latex-output-dir: Doc
execute: 
  echo: false
  warning: false
  error: false
---

```{r}
#| label: setup

library(knitr)
library(tidyverse)
# opts_knit$set(
#     echo = FALSE,
#     fig_path()
# )

library(kableExtra)
options(
    knitr.table.format = "latex",
    knitr.kable.NA = "")

prod_dir <- '../outputs/'

```


# No Splines

Tables [-@tbl-HAC-8x8] and [-@tbl-HAC-8x8-u], triangle and uniform Kernel HAC (@Conley1999).

```{r}
#| label: tbl-HAC-8x8
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, the **triangle** kernel HAC variance estimator for the standard error. No Splines. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


exe<-'8x8_no_cons_unif_bs_keep_'

tbl_quad_bs_s<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_slope.csv'
    )
)

kbl(
    tbl_quad_bs_s,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC'=ncol(tbl_quad_bs_s)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s))
)

```

```{r}
#| label: tbl-HAC-8x8-u
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, the **uniform** kernel HAC variance estimator for the standard error. No Splines. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's). 


tbl_quad_bs_s_u<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_slope_u.csv'
    )
)

kbl(
    tbl_quad_bs_s_u,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC'=ncol(tbl_quad_bs_s_u)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u))
)

```


# 8x8 Splines

## Uniform Splines

Tables [-@tbl-HAC-8x8-unif-bs] and [-@tbl-HAC-8x8-u-unif-bs], triangle and uniform Kernel HAC (@Conley1999) with an 8x8 step functions splines.


```{r}
#| label: tbl-HAC-8x8-unif-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **uniform** B-splines and the **triangle** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


exe<-'8x8_no_cons_unif_bs_keep_'

tbl_quad_bs_s<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope.csv'
    )
)

kbl(
    tbl_quad_bs_s,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Unif-BS'=ncol(tbl_quad_bs_s)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s))
)

```

```{r}
#| label: tbl-HAC-8x8-u-unif-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **uniform** B-splines and the **uniform** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


tbl_quad_bs_s_u<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u.csv'
    )
)

kbl(
    tbl_quad_bs_s_u,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Unif-BS'=ncol(tbl_quad_bs_s_u)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u))
)

```


```{r}
#| label: tbl-HAC-8x8-ci-unif-bs
#| tbl-cap: Confidence Interval length of using the **triangle** kernel HAC variance estimator for the standard error after adding an 8x8 **uniform** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).
#| eval: false
#| include: false

# exe<-'8x8_unif_splines_'

tbl_quad_bs_s_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Quad-BS'=ncol(tbl_quad_bs_s_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_ci))
)

```

```{r}
#| label: tbl-HAC-8x8-u-ci-unif-bs
#| tbl-cap: Confidence Interval length of using the **uniform** kernel HAC variance estimator for the standard error after adding an 8x8 **uniform** B-splines. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).
#| eval: false
#| include: false

tbl_quad_bs_s_u_ci<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u_ci.csv'
    )
)

kbl(
    tbl_quad_bs_s_u_ci,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u_ci)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Quad-BS'=ncol(tbl_quad_bs_s_u_ci)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u_ci))
)

```

## Quadratic Splines

Tables [-@tbl-HAC-8x8-Quad-bs] and [-@tbl-HAC-8x8-u-Quad-bs], triangle and uniform Kernel HAC (@Conley1999) with an 8x8 quadratic splines.


```{r}
#| label: tbl-HAC-8x8-Quad-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **quadratic** B-splines and the **triangle** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


exe<-'8x8_no_cons_quad_bs_'

tbl_quad_bs_s<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope.csv'
    )
)

kbl(
    tbl_quad_bs_s,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Tri-HAC+Quad-BS'=ncol(tbl_quad_bs_s)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s))
)

```

```{r}
#| label: tbl-HAC-8x8-u-Quad-bs
#| tbl-cap: Rejection frequencies testing the null hypothesis that the slope is statically different from the true value, zero, using an 8x8 **quadratic** B-splines and the **uniform** kernel HAC variance estimator for the standard error. The number of B-splines was fixed at 8x8. 200 simulations. **500** points. Column 'corr' shows the theoretical correlation at distance $h=0.1$, thus, $corr=\rho*\exp(-\frac{1}{\sqrt{2}})$. HR shows the rejection frequencies of the Heteroscedastic Robust Variance estimator (Stata's).


tbl_quad_bs_s_u<- read.csv(
    paste0(
        prod_dir,
        exe,
        'rej_freq_tab_kernel_bsplines_slope_u.csv'
    )
)

kbl(
    tbl_quad_bs_s_u,
    digits=3,
    booktabs=TRUE,
    position = 'htp',
    col.names = gsub("X","",names(tbl_quad_bs_s_u)),
    escape = FALSE
) %>%
add_header_above(
    c(' '=2, 'Unif-HAC+Quad-BS'=ncol(tbl_quad_bs_s_u)-6)
)%>%
add_header_above(
    c('Slope'=ncol(tbl_quad_bs_s_u))
)

```



# References {-}

::: {#refs}
:::